Topic Scores

### 2019-02-19 Topic Scores.Rmd
cuts rough code

student$course_score <- gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score)) %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )
```
###View
```{r View course}
View(student$topic_score)
View(student$course_score)
```
###Other comparison functions
```{r other functions}
#
##Binary
product <- function(a = gamma, b = B_score){
  X = a*b
}

```
### Comparing results
```{r}
bla %>%
  mutate(no= row_number())

b <- gamma_descriptions %>%
  full_join(student$topic_score, by="topic") %>%
  mutate(X = gamma*Beta_score) %>%
  arrange(desc(X))%>%
  mutate(no= row_number())

a %>% full_join(b, by="no") %>%
  mutate(equal= case_when(document.x==document.y~T,
                          T~F))
```

>>>>

student$course_score <- gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score)) %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )
```
###View
```{r View course}
View(student$topic_score)
View(student$course_score)
```
